%-------------------------
% Resume in Latex
% Author : Jojo Joseph
% Based off of: https://github.com/TheJojoJoseph/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Jojo Joseph } \\ \vspace{1pt}
    \small +91944-6300-967 $|$ \href{mailto:JojoJoseph11@gmail.com}{\underline{m200612@rajagiri.edu.in}} $|$ 
    \href{https://www.linkedin.com/in/jojojoseph/}{\underline{linkedin.com/in/jojojoseph/}} $|$
    \href{https://www.dynamiclithium.com/jojojoseph}{\underline{dynamiclithium.com/jojojoseph}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
  \resumeSubheading
      {Rajagiri School of Engineering and Technology }{APJ Abdul Kalam Technological University }
      {Masters of Technology in VLSI and Embedded system —  }{Jun. 2020 -- present}
    \resumeSubheading
      {Rajagiri School of Engineering and Technology }{APJ Abdul Kalam Technological University }
      {Bachelors of Technology in Electrical and Electronics Engg. — CGPA 6.9 }{Jun. 2015 -- May 2019}
       
    \resumeSubheading
      {Model Technical Higher Secondary }{IHRD }
      {Higher Secondary,2015 GPA 9.1}{Aug. 2013 -- May 2015}
      \resumeSubheading
      { Rajagiri Higher Secondary School }{Kalamassery }
      {Secondary Diplomas and Certificate - GPA 9.8}{Aug. 2001 -- May 2013}
     
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Embedded and Hardware Engineer : Full-stack developer }{Sept 2020 -- Feb 2020}
      {MEPITS INFO TECH Private Limited}{Kochi, IN}
      \resumeItemListStart
        \resumeItem{Developed and maintained Online LMS(learning management systems) and e-Commerce. www.superkitz.com.}
        \resumeItem{ Lead Engineerin various IoT CE products and Industrial Automation Projects under MEPITS}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Student Intern Electrical Eng.}{Jun. 2017 -- July 2017}
      {Henry Farad Private Limited(Subsidiary of GRACETEC)}{Kochi, IN}
      \resumeItemListStart
        \resumeItem{Worked as a Student Intern with their vps Lakeshore Hospital Project.}
        \resumeItem{Featured installation and charging of two 2000 KVA transformer to newly constructed block}
        \resumeItem{ complete electrical and network wiring of newly constructed block of the hospital.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    
     \resumeProjectHeading
          {\textbf{Optimizing the Convolution Operation to Accelerate DNN on FPGA} $|$ \emph{ML, CNN, Tensorflow, Python, Verilog }}{Feb 2021 -- April 2021}
          \resumeItemListStart
            \resumeItem{Developed a IP block design of optimized MAC block in Vivado (Verilog)}
            \resumeItem{Literature Survey on Convolution Operation on HLS(High Level Synthesis) in Vivado HLS}
            \resumeItem{Various CNN Accelerators and analysed and their performance quantified }
            \resumeItem{Documentation www.rsetcnnfpga.ml}
          \resumeItemListEnd
          
          
           \resumeProjectHeading
          {\textbf{COVID-19: Face Mask Detector with OpenCV, Keras/TensorFlow, and Deep Learning} $|$ \emph{ML,Keras/TensorFlow, Python, OpenCV }}{Feb 2021 -- March 2021}
          \resumeItemListStart
            \resumeItem{surveillance task performer with ML based detection software running on embedded platform: Raspberry pi }
            \resumeItem{ Detects the face from the image correctly and then identifies if it has a mask on it or not}
            \resumeItem{Model attains accuracy up to 95.77 \% and 94.58 \% respectively on two different datasets. }
            \resumeItem{ML,Keras/TensorFlow, Python, OpenCV }
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{SMART PEPPER} $|$ \emph{Python,RaspberryPi, ESP8266,STM32, NodeRED, C++, Cloud, Firebase}}{June 2018 -- 2019}
          \resumeItemListStart
          \resumeItem{Smart Metering System and Domestic Task Scheduling Under Dynamic Pricing Using the Multiple Knapsack Method}
            
            \resumeItem{optimally scheduling a set of residential appliances under day-ahead variable peak pricing in order to minimize the customer’s energy bill (and also, simultaneously spread out energy usage)}
            \resumeItem{Developed a full-stack web application using with ThinkSpeak MQTT API with Google FireBase}
            \resumeItem{multiple knapsack problem – which enables cheap and efficient solutions to the scheduling problem. (build on Raspberry Pi, STM32 and ESP8266)}
            \resumeItem{Documentation www.Smartpepper.ga}
          \resumeItemListEnd
     
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Verilog , Python, C/C++, HTML/CSS, SQL} \\
     \textbf{Frameworks}{: TensorFlow, WordPress, Google Firebase, BlockChain} \\
     \textbf{Developer Tools}{ Vivado, Vivado HLS , MathLab, Google Cloud Platform, VS Code , PyCharm, Proteus} \\
     \textbf{Libraries}{: OpenCV, MQTT , Keras, NumPy, Matplotlib} \\
     \textbf{Hardware Platform}{: STM32, ESP8266/32 , RaspberryPI , Arduino}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
